SaPaFigures

### 2022-02-23 R/PaperFigures.Rmd
Added correct labels to inner vs outer

```{r figure 1}
#Figure 1A CFU data wt
#####
#CFU data from Carolyn
CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CFU_wound_All_dataTidy.csv",header = TRUE)
CFUdata$Condition<-as.factor(CFUdata$Condition)
   CFUdata$Day<-as.factor(CFUdata$Day)
   CFUdata$Species<-as.factor(CFUdata$Species)
   CFUdata$Strain<-as.factor(CFUdata$Strain)
CFUdata$Condition <- factor(CFUdata$Condition, levels = c("mono", "co-wt", "co-pqsL"))
CFUstats<-CFUdata%>%group_by(Species,Condition,Strain,Day) %>% mutate(MeanCFU = mean(CFU), SECFU = std.error(CFU))
CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))
PlotCFUs<- function(){
ggplot()+
  geom_col(data = CFUstats %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),aes(x=Species,y=MeanCFU, fill = Condition),
           size=3,position = position_dodge( width = .9))+

@@

#Figure 2A: Percent CFU inner wound
##### 
CFUInOutData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/Inside_Outside_CFUcm2_Day4Tidy.csv",header = TRUE)
CFUInOutData<-Filter(function(x)!all(is.na(x)), CFUInOutData)#this is to remove columns with NA
CFUInOutData <- na.omit(CFUInOutData) #removing rows with NA
CFUInOutData$Condition<-as.factor(CFUInOutData$Condition)
CFUInOutData$Sample<-as.factor(CFUInOutData$Sample)
CFUInOutData$Species<-as.factor(CFUInOutData$Species)
CFUInOutData$Strain<-as.factor(CFUInOutData$Strain)

CFUInOutDataPost<-CFUInOutData %>% mutate(CFU.Inside = Inside.Bandage+Inside.Tissue, CFU.Outside = Outside.Tissue+Outside.Bandage) %>% mutate(PercentIn = 100*CFU.Outside/(CFU.Inside+CFU.Outside))

@@

PlotInCFUs<- function(){
  ggplot()+
    geom_col(data = CFUInOutStatsWt,aes(x=Species,y=meanInPercent, fill = Condition),size=3,position = position_dodge( width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent-SEInPercent), ymax = (meanInPercent+SEInPercent), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+
    scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
  }
figure2A<-PlotInCFUs()
figure2A

@@

PlotInCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUInOutPostWt,aes(x=Species,y=PercentIn, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent), ymax = (meanInPercent), group = Condition),width = .4, size=.5,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,75))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure2A2<-PlotInCFUs2()
figure2A2

>>>>

```{r figure 1}
#Figure 1A CFU data wt
#####
#CFU data from Carolyn
CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/CFU_wound_All_dataTidy.csv",header = TRUE)
CFUdata$Condition<-as.factor(CFUdata$Condition)
   CFUdata$Day<-as.factor(CFUdata$Day)
   CFUdata$Species<-as.factor(CFUdata$Species)
   CFUdata$Strain<-as.factor(CFUdata$Strain)
CFUdata$Condition <- factor(CFUdata$Condition, levels = c("mono", "co-wt", "co-pqsL"))
CFUstats<-CFUdata%>%group_by(Species,Condition,Strain,Day) %>% mutate(MeanCFU = mean(CFU), SECFU = std.error(CFU))
CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))

PlotCFUs<- function(){
ggplot()+
  geom_col(data = CFUstats %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),aes(x=Species,y=MeanCFU, fill = Condition),
           size=3,position = position_dodge( width = .9))+

@@

#Figure 2A: Percent CFU inner wound
##### 
CFUInOutData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/Inside_Outside_CFUcm2_Day4Tidy.csv",header = TRUE)
CFUInOutData<-Filter(function(x)!all(is.na(x)), CFUInOutData)#this is to remove columns with NA
CFUInOutData <- na.omit(CFUInOutData) #removing rows with NA
CFUInOutData$Condition<-as.factor(CFUInOutData$Condition)
CFUInOutData$Sample<-as.factor(CFUInOutData$Sample)
CFUInOutData$Species<-as.factor(CFUInOutData$Species)
CFUInOutData$Strain<-as.factor(CFUInOutData$Strain)

CFUInOutDataPost<-CFUInOutData %>% mutate(CFU.Inside = Inside.Bandage+Inside.Tissue, CFU.Outside = Outside.Tissue+Outside.Bandage) %>% mutate(PercentIn = 100*CFU.Inside/(CFU.Inside+CFU.Outside))

@@

PlotInCFUs<- function(){
  ggplot()+
    geom_col(data = CFUInOutStatsWt,aes(x=Species,y=meanInPercent, fill = Condition),size=3,position = position_dodge( width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent-SEInPercent), ymax = (meanInPercent+SEInPercent), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+
    scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in wound core")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
  }
figure2A<-PlotInCFUs()
figure2A

@@

PlotInCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUInOutPostWt,aes(x=Species,y=PercentIn, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent), ymax = (meanInPercent), group = Condition),width = .4, size=.5,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,100))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure2A2<-PlotInCFUs2()
figure2A2
